\documentclass{article}

\title{A game theoretic model of the behavioural gaming that takes place at the 
EMS - ED interface}
\author{Michalis Panayides}

\begin{document}

\maketitle
\begin{abstract}
    
    Operational Research (OR) techniques provide a toolkit of mathematical 
    modelling approaches that are routinely used for problem solving in many
    sectors. Healthcare is considered to be one of such sectors where, in recent
    years, OR has found several applications.
    
    Emergency departments (EDs) in hospitals are usually under pressure to 
    achieve a target amount of time that describes the arrival of patients and 
    the time it takes to receive treatment. For example in the UK this is often 
    set as 95\% of patients to be treated within 4 hours. There is empirical 
    evidence to suggest that imposing targets in the ED results in gaming at the 
    interface of care between the EMS and ED. 

    This study explores the impact that this effect may have on an ambulance's 
    utilisation and their ability to respond to emergency calls. More 
    specifically multiple scenarios are examined where an ambulance service 
    needs to distribute patients between neighbouring hospitals. The interaction 
    between the hospitals and the ambulance service is defined in a game 
    theoretic framework where the ambulance service has to decide how many 
    patients to distribute to each hospital in order to minimise the occurrence 
    of this effect. The methodology involves the use of a queueing model for 
    each hospital that is used to inform the decision process of the ambulance 
    service so as to create a game for which the Nash Equilibria can be 
    calculated. Numerous decisions are taken by both patients and staff alike 
    that determine the level of workflow and the patient pathway.
    
    This study aims to explore the use of a queueing theoretic model with two 
    waiting spaces and use it to inform a game theoretic system that captures
    the emergent behaviour between the EMS and ED.
    
\end{abstract}
    
\end{document}


